---
title: "Recommendation Workflow"
output: rmarkdown::html_vignette
vignette: |
  %\VignetteIndexEntry{Recommendation Workflow} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
---

```{r setup-vignette, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
if ( file.exists("not_included/daniel_env.R")) {
  source ("not_included/daniel_env.R")
} else {
  source ("../not_included/daniel_env.R")
}

listen_local_artists <- readRDS("not_included/listen_local_artists.rds")
artist_distances     <- readRDS("not_included/artist_distances.rds")
local_genre_table    <- readRDS("not_included/local_genre_table.rds")
artist_genre_table   <- readRDS("not_included/artist_genre_table.rds")

```

```{r startup}
library(spotifyrecommendations)
slovakia_indie_playlist_id       <- "1E8vQ9Bt4bRKWm0NTzSMt2"
slovakia_top_50_playlist_id      <- "6WrpeNyqtoq6PEDXyuamGt"
sound_of_dutch_indie_playlist_id <- "2pSeH1YQCSICs2knjs7e5o"

token  <- get_spotify_access_token()
```


```{r listen_local_artists}
data ("listen_local_artists")

listen_local_artists %>%
  dplyr::sample_n(12)
```

The `?get_playlist` information uses `?get_release_country`

```{r get_playlist_information}

slovakia_indie_playlist_info <- get_playlist_information(
  playlist_id  = slovakia_indie_playlist_id, 
  authorization = token
  )

slovakia_top_50_info <- get_playlist_information(
  playlist_id  = slovakia_top_50_playlist_id, 
  authorization = token
  )

dutch_indie_info <- get_playlist_information(
  playlist_id  = sound_of_dutch_indie_playlist_id, 
  authorization = token
  )

slovakia_indie_playlist_info$user_playlist_artists %>% head ()
slovakia_indie_playlist_info$user_playlist_tracks  %>% head ()
```

## Initial recommendations 

The function `initial_recommendations()` returns a tibble of recommendations. `recommendations_by_tracks$target_artists` contains a logical vector, identifying the tracks that are among `target_ids`.

```{r initial_recommendations}

sk_artist_ids <- get_national_artist_ids("sk")

initial_slovak_indie <- initial_recommendations(
  playlist_information = slovakia_indie_playlist_info, 
  target_ids = sk_artist_ids, 
  authorization = token )

initial_slovak_hits <- initial_recommendations(
  playlist_information = slovakia_top_50_info, 
  target_ids = sk_artist_ids, 
  authorization = token )

initial_dutch_indie <- initial_recommendations(
  playlist_information = dutch_indie_info, 
  target_ids = sk_artist_ids, 
  authorization = token )
```


```{r}
sum(initial_slovak_indie$release_country_code == "sk")
sum(initial_slovak_indie$target_artists)
```



```{r}
sum(initial_slovak_hits$release_country_code == "sk")
sum(initial_slovak_hits$target_artists)
```



```{r}
sum(initial_dutch_indie$release_country_code == "sk")
sum(initial_dutch_indie$target_artists)
```

## Recommendations Based On Artist Similarity

```{r recommend-by-artist}
recommended_by_artist_similarity <- get_local_artist_recommendations(
  user_playlist_artists = slovakia_indie_playlist_info$user_playlist_artists$id,
  n_rec = 5
  )
```

Behind the scenes, first of all the similar artists are defined.

```{r get_local_artist_recommendations}

target_ids <- listen_local_artists %>%
  filter ( target_nationality == "sk") %>%
  select ( spotify_artist_id ) %>% unlist () %>% as.character()

new_artists_spotify_artist_id <- get_local_artist_recommendations(
  user_playlist_artists = slovakia_indie_playlist_info$user_playlist_artists$id,
  target_ids = target_ids,
  n = 5,
  authorization = NULL )
```

Then the new recommended artists' nearest tracks are defined:

```{r get_local_artist_recommendations}
tracks_by_artist_similarity <- lapply ( recommended_by_artist_similarity,
                                        purrr::possibly(get_artist_audio_features, NULL))

tracks_by_artist_similarity <- do.call( rbind, tracks_by_artist_similarity  )

local_recommendations_by_artist <- get_nearest_tracks(
  user_playlist_info$user_playlist_tracks,
  tracks_by_artist_similarity )
```

## Recommendations Based On Genre

```{r recommend-by-genre}

dutch_artists_by_genre <- get_artist_genre(
  user_playlist_artists = dutch_indie_info$user_playlist_artists
  )

user_artists_by_genre <- get_artist_genre(
    user_playlist_artists = dutch_indie_info$user_playlist_artists
  )

  ## recommend artists by genre first
recommended_by_genre <- get_artist_recommendations_genre(
    artists_by_genre = user_artists_by_genre,
    target_nationality = target_nationality
  )

tracks_by_genre_similarity <- lapply (
    recommended_by_genre,
    purrr::possibly(get_artist_audio_features, NULL)) %>%
  do.call( rbind, .)

get_nearest_tracks(
    user_tracks = user_playlist_info$user_playlist_tracks,
    tracks_by_genre_similarity,
    n = 6 )
```


## Track Recommendatinos

```{r}
vars_to_select <- c( "id", "name", "popularity", 
                    "uri", "external_ids.isrc",
                    "release_country_code", 
                    "target_artists")

get_local_recommendations(
    playlist_id = sound_of_dutch_indie_playlist_id,
    target_nationality = "sk",
    recommendation_type = "artists",
    limit = 20,
    n = 4,
    silent = TRUE,
    authorization = NULL )
```
```{r}
start_time <- Sys.time()
slovak_indie_based <- get_local_recommendations(
  playlist_id = "1E8vQ9Bt4bRKWm0NTzSMt2",
  recommendation_type = "release"
)
Sys.time()-start_time
```


```{r}
start_time <- Sys.time()
global_top_50 <- get_local_recommendations(
  playlist_id = "1KNl4AYfgZtOVm9KHkhPTF",
  recommendation_type = 'artists' 
)
Sys.time()-start_time
```


```{r}
start_time <- Sys.time()
french_post_rock <- get_local_recommendations(
  user_playlist_id = "66GxbkUX9OZikMgn338pz6", 
  authorization = token 
)
Sys.time()-start_time
```

```{r}
start_time <- Sys.time()
french_rock <- get_local_recommendations(
    user_playlist_id = "6uL4zN0tryTmOsrhcknaIS"
)
Sys.time()-start_time
```


```{r}
start_time <- Sys.time()
french_rock <- get_local_recommendations(
    user_playlist_id = "0qJTEzbjENk61TtYeqFxfq"
)
Sys.time()-start_time
```
